Bootstrap learning via modular concept discovery

### 2013-01-28 drafts/ijcai2013/ijcai13.tex
Changes.
Changes including adding EX3

@@

\begin{figure}
\begin{subfigure}[Before]{0.45\linewidth}
\includegraphics[width=\linewidth]{figures/learningCurves2.pdf}
\end{subfigure}
\begin{subfigure}[After]{0.45\linewidth}
\includegraphics[width=\linewidth]{figures/performanceVsFrontierSize2.pdf}
\end{subfigure}
\caption{(a) Average learning curves as we vary the frontier size. (b)
  Percent of tasks solved at iteration 15 as a function of frontier
  size.}
\label{fig:symreg} 
\end{figure}

>>>>

Let's assume there is a distribution over tasks in our domain
$p_{task}(\dot)$ and that these tasks are drawn $i.i.d$ from this
distribution. We can frame our goal as finding an ordering on programs
$w : \mathcal{L} \rightarrow (1, \dots)$ such that if we search for programs
according to $w$ then the expected number of programs we need to
inspect is minimized. But this ordering is exactly that which is
defined by $p_{task}$. Namely, let $e_1, e_2 \in \mathcal{L}$ solve
tasks $t1, t2$ respectively. Then we want $w(e_1) > w(e_2) $ iff $
p_{task}(t_1) > p_{task}(t_2)$. One way to achieve this is that for every
$e \in \mathcal{L}$ that solves task $t$, we define $w$ to be ordering
according to the distribution $p_\mathcal{L}(e) \propto p_{task}(t)$.

@@

\begin{figure}
\begin{subfigure}[Before]{.6\linewidth}
%% \includegraphics[width=\linewidth]{figures/learningCurves2.pdf}
\includegraphics[width=\linewidth]{figures/symreg3frontiers.pdf}
\end{subfigure}
%% \begin{subfigure}[After]{0.45\linewidth}
%% \includegraphics[width=\linewidth]{figures/performanceVsFrontierSize2.pdf}
%% \end{subfigure}
\caption{(a) Average learning curves as we vary the frontier size. (b)
  Percent of tasks solved at iteration 15 as a function of frontier
  size.}
\label{fig:symreg} 
\end{figure}
